Visualizations for the manuscript

### 2022-03-29 metanalysis_visualization/manuscript_Figures.Rmd
acronyms in plots changed by long version

```{r libraries, message=FALSE, warning=FALSE, results='hide'}
# Install packages
paket <- function(pak){
  new_pak <- pak[!(pak %in% rownames(installed.packages()))]
  if (length(new_pak)) 
    install.packages(new_pak, dependencies = TRUE,repos="https://cloud.r-project.org/")
  sapply(pak, library, character.only = TRUE)
}
listOfPackages <- c("tidyverse", "tidyr","devtools","RColorBrewer", "knitr", "kableExtra", "tsModel", "gridExtra", "dplyr", "metafor", "meta", "viridis", "UpSetR", "scales", "EHRtemporalVariability")
paket(listOfPackages)

@@

names_site_id <- unique(df_coefficients_boot$siteid)

plot_annotations <- df_coefficients_boot %>% 
  group_by(siteid) %>% 
  group_map( annotation_function ) %>% 
  set_names(names_site_id) %>% 
  unlist()
plot_annotations_df <- data.frame(
  siteid = names(plot_annotations), 
  label = plot_annotations
)
```

```{r}
### January 19-May 21
ggplot(bootstrapped_fitted_all, aes(x = time_p, y = predicted, group = interaction(iteration, period))) +
  facet_wrap("siteid", scales = "free_y") +
  geom_line(aes(color = period),
            alpha = 0.03) +
  geom_line(data = quantile_bootstrapped_fitted_all,
            aes(y = value, group = interaction(quantiles, period)),
            linetype = "dashed") +
  geom_line(data = quantile_bootstrapped_fitted_all[quantile_bootstrapped_fitted_all$quantiles == "50%", ],
            aes(y = value, group = period)) +
  geom_point(data = count_icd_all_boot,
             aes(y = percentage, group=NULL),
             alpha = 0.5) +
  scale_colour_manual(values = cbPalette) +
  guides(color = guide_legend(override.aes = list(alpha = 1))) +
  geom_label(data = plot_annotations_df, 
             aes(label=label), 
            x = -Inf,
            y = +Inf,
            hjust = 0,
            vjust = 1,
            size = 4,
            inherit.aes = FALSE) +
  labs(title = "Interrupted Time Series Analysis: Percentage of patients with psychiatric conditions",
       subtitle = "Parametric bootstrap estimation: (1000 iterations)",
       x = "Calendar dates",
       y = "Percentage",
       color = "Period") +
  theme(strip.text = element_text(size = 10),
        axis.text.x = element_text(size = 8), 
        axis.text.y = element_text(size = 8), 
        axis.title.x = element_text(size = 8),
        axis.title.y = element_text(size = 8),
        title = element_text(size = 14),
        plot.subtitle = element_text(size = 12, face = "italic")) 
ggsave("boostrapped_all_extended.png", height = 20, width = 32, units = "cm")
```

```{r}
### Feb 19-April 21
ggplot(bootstrapped_fitted_all, aes(x = time_p, y = predicted, group = interaction(iteration, period))) +
  facet_wrap("siteid", scales = "free_y") +
  geom_line(aes(color = period),
            alpha = 0.03) +
  geom_line(data = quantile_bootstrapped_fitted_all,
            aes(y = value, group = interaction(quantiles, period)),
            linetype = "dashed") +
  geom_line(data = quantile_bootstrapped_fitted_all[quantile_bootstrapped_fitted_all$quantiles == "50%", ],
            aes(y = value, group = period)) +
  geom_point(data = patient_count_psy_period_psy_all,
             aes(y = percentage, group=NULL),
             alpha = 0.5) +
  scale_colour_manual(values = cbPalette) +
  guides(color = guide_legend(override.aes = list(alpha = 1))) +
  geom_label(data = plot_annotations_df, 
             aes(label=label), 
            x = -Inf,
            y = +Inf,
            hjust = 0,
            vjust = 1,
            size = 4,
            inherit.aes = FALSE) +
  labs(title = "Interrupted Time Series Analysis: Percentage of patients with psychiatric conditions",
       subtitle = "Parametric bootstrap estimation: (1000 iterations)",
       x = "Calendar dates",
       y = "Percentage",
       color = "Period") +
  theme(strip.text = element_text(size = 10),
        axis.text.x = element_text(size = 8), 
        axis.text.y = element_text(size = 8), 
        axis.title.x = element_text(size = 8),
        axis.title.y = element_text(size = 8),
        title = element_text(size = 14),
        plot.subtitle = element_text(size = 12, face = "italic")) 
ggsave("boostrapped_all.png", height = 20, width = 32, units = "cm")
```

@@

```{r}
trends_siteid <- df_coefficients_boot %>% 
  group_by(siteid) %>% 
  summarise(mean_boot = mean(`periodduring_pandemic:time`),
            observed = unique(observed_diff),
            var_boot = var(`periodduring_pandemic:time`), 
            z = mean_boot / sqrt(var_boot), 
            pvalue = pnorm(z, lower.tail = FALSE)*2 )
```

@@

metafor::forest(model_meta_siteid,
                slab = trends_siteid$siteid,
                plim = c(1, NA),
                order = "obs",
                showweights = TRUE,
                header="Sites",
                mlab="Overall periods' slope differences")
```

```{r}
trends_country <- trends_siteid %>% 
  left_join(country_map, by = "siteid") %>% 
  group_by(country) %>% 
  group_modify(.f = function(x, ...) {
    as.data.frame(
      predict(rma(yi = observed, 
                vi = var_boot,
                measure = "MN",
                method = "DL",
                data = x))
    )
  },
  .keep = TRUE)

@@

fig = plotDataTemporalMap(x)

@@

#### At site level
```{r}
library(reshape2)

counts <- count_icd_all %>%
  mutate( time = seq_along(time_p),
         month_year = format(time_p, "%m")) %>%
  select( siteid, time_p, time, month_year, count_psy_patients = count_psy, total_cases = count_icd )

counts2 <- reshape2::melt(counts ,  id.vars = c('siteid', 'time_p', 'time','month_year'), variable.name = 'group')
counts2$group <- gsub("count_psy_patients", "patients with psychiatric conditions", counts2$group )
counts2$group <- gsub("total_cases", "total number of patients", counts2$group )

counts2 %>% ggplot( aes( x= as.Date( time_p ), y = value, group= group )) +
  geom_point( aes( shape= group, color = group )) +
  facet_wrap2("siteid", axes = "all", scales ="free") + 
  geom_vline(xintercept = as.Date(pandemic_start_date), linetype = "dashed") +
  labs(x ="", y = "number of patients")+
  scale_x_date(breaks = "1 month", labels=date_format("%b-%y"), expand=c(0.03,0)) +
  scale_color_manual( values = cbPalette ) + 
  theme(axis.text.x=element_text(angle = 45, hjust=1, size = 6), 
        strip.text = element_text(size = 10, face = "bold"),
        panel.grid.major = element_blank(), panel.grid.minor = element_blank(), strip.background = element_blank(),
        panel.border = element_rect(colour = "black", fill = NA), 
        legend.position="bottom")
```

>>>>

```{r libraries, message=FALSE, warning=FALSE, results='hide'}
# Install packages
paket <- function(pak){
  new_pak <- pak[!(pak %in% rownames(installed.packages()))]
  if (length(new_pak)) 
    install.packages(new_pak, dependencies = TRUE,repos="https://cloud.r-project.org/")
  sapply(pak, library, character.only = TRUE)
}
listOfPackages <- c("tidyverse", "tidyr","devtools","RColorBrewer", "knitr", "kableExtra", "tsModel", "gridExtra", "dplyr", "metafor", "meta", "viridis", "UpSetR", "scales", "EHRtemporalVariability", "plotly")
paket(listOfPackages)

@@

df_coefficients_boot <- df_coefficients_boot %>%
  left_join( country_map )

names_site_id <- unique(df_coefficients_boot$plotsLabel)

plot_annotations <- df_coefficients_boot %>% 
  group_by(plotsLabel) %>% 
  group_map( annotation_function ) %>% 
  set_names(names_site_id) %>% 
  unlist()
plot_annotations_df <- data.frame(
  plotsLabel = names(plot_annotations), 
  label = plot_annotations
)
```

```{r}
### January 19-May 21
bootstrapped_fitted_all <- bootstrapped_fitted_all %>%
  left_join( country_map )

quantile_bootstrapped_fitted_all <- quantile_bootstrapped_fitted_all %>%
  left_join( country_map )

count_icd_all_boot <- count_icd_all_boot %>%
  left_join( country_map )

ggplot(bootstrapped_fitted_all, aes(x = time_p, y = predicted, group = interaction(iteration, period))) +
  facet_wrap("plotsLabel", scales = "free_y", labeller = label_wrap_gen(width = 35,multi_line = TRUE)) +
  geom_line(aes(color = period),
            alpha = 0.03) +
  geom_line(data = quantile_bootstrapped_fitted_all,
            aes(y = value, group = interaction(quantiles, period)),
            linetype = "dashed") +
  geom_line(data = quantile_bootstrapped_fitted_all[quantile_bootstrapped_fitted_all$quantiles == "50%", ],
            aes(y = value, group = period)) +
  geom_point(data = count_icd_all_boot,
             aes(y = percentage, group=NULL),
             alpha = 0.5) +
  scale_colour_manual(values = cbPalette) +
  guides(color = guide_legend(override.aes = list(alpha = 1))) +
  geom_label(data = plot_annotations_df, 
             aes(label=label), 
            x = -Inf,
            y = +Inf,
            hjust = 0,
            vjust = 1,
            size = 4,
            inherit.aes = FALSE) +
  labs(title = "Interrupted Time Series Analysis: Percentage of patients with psychiatric conditions",
       subtitle = "Parametric bootstrap estimation: (1000 iterations)",
       x = "Calendar dates",
       y = "Percentage",
       color = "Period") +
  theme(strip.text = element_text(size = 10),
        axis.text.x = element_text(size = 8), 
        axis.text.y = element_text(size = 8), 
        axis.title.x = element_text(size = 8),
        axis.title.y = element_text(size = 8),
        title = element_text(size = 14),
        plot.subtitle = element_text(size = 12, face = "italic")) 
ggsave("boostrapped_all_extended.png", height = 20, width = 32, units = "cm")
```

```{r}
### Feb 19-April 21
patient_count_psy_period_psy_all <- patient_count_psy_period_psy_all %>%
  left_join( country_map )

ggplot(bootstrapped_fitted_all, aes(x = time_p, y = predicted, group = interaction(iteration, period))) +
  facet_wrap("plotsLabel", scales = "free_y", labeller = label_wrap_gen(width = 35,multi_line = TRUE)) +
  geom_line(aes(color = period),
            alpha = 0.03) +
  geom_line(data = quantile_bootstrapped_fitted_all,
            aes(y = value, group = interaction(quantiles, period)),
            linetype = "dashed") +
  geom_line(data = quantile_bootstrapped_fitted_all[quantile_bootstrapped_fitted_all$quantiles == "50%", ],
            aes(y = value, group = period)) +
  geom_point(data = patient_count_psy_period_psy_all,
             aes(y = percentage, group=NULL),
             alpha = 0.5) +
  scale_colour_manual(values = cbPalette) +
  guides(color = guide_legend(override.aes = list(alpha = 1))) +
  geom_label(data = plot_annotations_df, 
             aes(label=label), 
            x = -Inf,
            y = +Inf,
            hjust = 0,
            vjust = 1,
            size = 4,
            inherit.aes = FALSE) +
  labs(title = "Interrupted Time Series Analysis: Percentage of patients with psychiatric conditions",
       subtitle = "Parametric bootstrap estimation: (1000 iterations)",
       x = "Calendar dates",
       y = "Percentage",
       color = "Period") +
  theme(strip.text = element_text(size = 10),
        axis.text.x = element_text(size = 8), 
        axis.text.y = element_text(size = 8), 
        axis.title.x = element_text(size = 8),
        axis.title.y = element_text(size = 8),
        title = element_text(size = 14),
        plot.subtitle = element_text(size = 12, face = "italic")) 
ggsave("boostrapped_all.png", height = 20, width = 32, units = "cm")
```

@@

```{r}
trends_siteid <- df_coefficients_boot %>% 
  group_by(plotsLabel) %>% 
  summarise(mean_boot = mean(`periodduring_pandemic:time`),
            observed = unique(observed_diff),
            var_boot = var(`periodduring_pandemic:time`), 
            z = mean_boot / sqrt(var_boot), 
            pvalue = pnorm(z, lower.tail = FALSE)*2 )
```

@@

metafor::forest(model_meta_siteid,
                slab = trends_siteid$plotsLabel,
                plim = c(1, NA),
                order = "obs",
                cex=0.7,
                showweights = TRUE,
                header="Sites",
                mlab="Overall periods' slope differences")
```

```{r}
trends_country <- trends_siteid %>% 
  left_join(country_map, by = "plotsLabel") %>% 
  group_by(country) %>% 
  group_modify(.f = function(x, ...) {
    as.data.frame(
      predict(rma(yi = observed, 
                vi = var_boot,
                measure = "MN",
                method = "DL",
                data = x))
    )
  },
  .keep = TRUE)

@@

fig = plotDataTemporalMap(tempVariabilityInput, absolute = TRUE)

@@

#### At site level
```{r}
library(reshape2)
count_icd_all <- count_icd_all %>%
  left_join( country_map )

counts <- count_icd_all %>%
  mutate( time = seq_along(time_p),
         month_year = format(time_p, "%m")) %>%
  select( plotsLabel, time_p, time, month_year, count_psy_patients = count_psy, total_cases = count_icd )

counts2 <- reshape2::melt(counts ,  id.vars = c('plotsLabel', 'time_p', 'time','month_year'), variable.name = 'group')
counts2$group <- gsub("count_psy_patients", "patients with psychiatric conditions", counts2$group )
counts2$group <- gsub("total_cases", "total number of patients", counts2$group )

counts2 %>% ggplot( aes( x= as.Date( time_p ), y = value, group= group )) +
  geom_point( aes( shape= group, color = group )) +
  facet_wrap2("plotsLabel", axes = "all", scales ="free", labeller = label_wrap_gen(width = 35,multi_line = TRUE)) + 
  geom_vline(xintercept = as.Date(pandemic_start_date), linetype = "dashed") +
  labs(x ="", y = "number of patients")+
  scale_x_date(breaks = "1 month", labels=date_format("%b-%y"), expand=c(0.03,0)) +
  scale_color_manual( values = cbPalette ) + 
  theme(axis.text.x=element_text(angle = 45, hjust=1, size = 6), 
        strip.text = element_text(size = 10, face = "bold"),
        panel.grid.major = element_blank(), panel.grid.minor = element_blank(), strip.background = element_blank(),
        panel.border = element_rect(colour = "black", fill = NA), 
        legend.position="bottom")
```
